Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-10-16 SupportingInformation.Rmd
reply : Lawrence comment...continued

  m<-matrix(NA,1,12)
  colnames(m)<-c("Indep.p","AIC-best.copula","Highest.AICw",
                 "N.AICw","p.CvM","p.KS",
                 "LT.model.avg","UT.model.avg","(LT-UT).model.avg",
                 "Rank.Pl.K","Rank.Pu.K","Rank.Pl-Pu.K")
  m<-as.data.frame(m)

  m$Indep.p<-round(r$IndepTestRes,3)
  m$`AIC-best.copula`<-r$InfCritRes$copname[which.min(r$InfCritRes$AIC)]
  m$Highest.AICw<-round(max(r$InfCritRes$AICw),3)
  m$N.AICw<-round(r$InfCritRes$AICw[1],3)
  m$p.CvM<-r$GofRes_CvM
  m$p.KS<-r$GofRes_KS
  m$LT.model.avg<-round(r$relLTdep_AICw,3)
  m$UT.model.avg<-round(r$relUTdep_AICw,3)
  m$`(LT-UT).model.avg`<-m$LT.model.avg-m$UT.model.avg
  m$Rank.Pl.K<-rs$Rank_Pl_K
  m$Rank.Pu.K<-rs$Rank_Pu_K
  m$`Rank.Pl-Pu.K`<-rs$Rank_PlmPu_K
  mt<-as.data.frame(t(m))
  return(mt)

@@

```{r cause4copula_pGOF_500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf", width=8, height=6)
op<-par(mfrow=c(2,2))

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "spearman",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="spearman",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "spearman",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="spearman",num_keep_last=500,BS=1000)

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "kendall",num_keep_last=500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="kendall",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "kendall",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="kendall",num_keep_last=500,BS=1000)

@@

op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 1, 0, 0), new = TRUE)
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("top", c("noise", "population", "p_CvM", "p_KS"), col = c("red", "blue", "magenta", "green2"),
       cex = 1.5, pch = c(2, 6, 16, 16), xpd = TRUE, horiz = TRUE, inset = c(0,0), 
       bty = "n") 
par(op)
dev.off()
```

```{r cause4copula_pGOF_2500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# I need to fix that SG_kendall ylimit error : I think I fixed it
#----------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf", width=8, height=6)
op<-par(mfrow=c(2,2))

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "spearman",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="spearman",num_keep_last=2500,BS=1000)

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "kendall",num_keep_last=2500,BS=1000)
Plotter_Cause4copula_GOF(N=5000,fcode=13,method="kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="kendall",num_keep_last=2500,BS=1000)

op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0), new = TRUE)
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("top", c("noise", "population", "p_CvM", "p_KS"), col = c("red", "blue", "magenta", "green2"),
       cex = 1.5, pch = c(2, 6, 16, 16), xpd = TRUE, horiz = TRUE, inset = c(0,0), 
       bty = "n") 
par(op)
dev.off()
```

```{r cause4copula_stat, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
pdf("./Results/Cause4copula_results/Clayton_spearman.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()

pdf("./Results/Cause4copula_results/Clayton_kendall.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="kendall",lb=0,ub=0.1,num_keep_last=500)
dev.off()

pdf("./Results/Cause4copula_results/SClayton_spearman.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()

pdf("./Results/Cause4copula_results/SClayton_kendall.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="kendall",lb=0,ub=0.1,num_keep_last=500)
dev.off()

pdf("./Results/Cause4copula_results/Gumbel_spearman.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=4,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()

pdf("./Results/Cause4copula_results/Gumbel_kendall.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=4,method="kendall",lb=0,ub=0.1,num_keep_last=500)
dev.off()

pdf("./Results/Cause4copula_results/SGumbel_spearman.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=14,method="spearman",lb=0,ub=0.1,num_keep_last=500)
dev.off()

pdf("./Results/Cause4copula_results/SGumbel_kendall.pdf")
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=14,method="kendall",lb=0,ub=0.1,num_keep_last=500)
dev.off()
```

>>>>

  m<-matrix(NA,1,10)
  colnames(m)<-c("p.Independence.test","minimumAIC.bestfit.copula","Bestfit.copula.AICw",
                 "Normal.copula.AICw","p.CvM","p.KS",
                 "LT.model.avg","UT.model.avg","(LT-UT).model.avg",
                 "Rank.(Pl-Pu)")
  m<-as.data.frame(m)

  m$p.Independence.test<-round(r$IndepTestRes,3)
  m$minimumAIC.bestfit.copula<-r$InfCritRes$copname[which.min(r$InfCritRes$AIC)]
  m$Bestfit.copula.AICw<-round(max(r$InfCritRes$AICw),3)
  m$Normal.copula.AICw<-round(r$InfCritRes$AICw[1],3)
  m$p.CvM<-r$GofRes_CvM
  m$p.KS<-r$GofRes_KS
  m$LT.model.avg<-round(r$relLTdep_AICw,3)
  m$UT.model.avg<-round(r$relUTdep_AICw,3)
  m$`(LT-UT).model.avg`<-m$LT.model.avg-m$UT.model.avg
  m$`Rank.(Pl-Pu)`<-rs$Rank_PlmPu_K
  mt<-as.data.frame(t(m))
  return(mt)

@@

```{r cause4copula_pGOF_500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf", width=8, height=3)
op<-par(mfrow=c(1,2))

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "spearman",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=13,method="spearman",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "spearman",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="spearman",num_keep_last=500,BS=1000)

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "kendall",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=13,method="kendall",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "kendall",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="kendall",num_keep_last=500,BS=1000)

@@

op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 1, 0, 0), new = TRUE)
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("top", c("noise copula,", "population copula,",  "Gof test : p-value(CvM),", "Gof test : p-value(KS)"), col = c("red","blue", "magenta", "green2"),
       cex = 0.9, pch = c(2, 6, 16, 16), xpd = TRUE, horiz = TRUE, inset = c(0,0),
       bty = "n") 
par(op)
dev.off()
```

```{r cause4copula_pGOF_2500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# I need to fix that SG_kendall ylimit error : I think I fixed it
#----------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf", width=8, height=3)
op<-par(mfrow=c(2,2))

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=13,method="spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="spearman",num_keep_last=2500,BS=1000)

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=13,method="kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="kendall",num_keep_last=2500,BS=1000)

op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 1, 0, 0), new = TRUE)
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("top", c("noise copula,", "population copula,",  "Gof test : p-value(CvM),", "Gof test : p-value(KS)"), col = c("red","blue", "magenta", "green2"),
       cex = 0.9, pch = c(2, 6, 16, 16), xpd = TRUE, horiz = TRUE, inset = c(0,0),
       bty = "n") 
par(op)
dev.off()
```

```{r cause4copula_stat, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
resloc<-"./Results/Cause4copula_results/"
if (!dir.exists(paste(resloc,"Cause4copula_stat_results",sep=""))){
  dir.create(paste(resloc,"Cause4copula_stat_results",sep=""))
  resloc<-"./Results/Cause4copula_results/Cause4copula_stat_results/"
}
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc)                    
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=4,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=4,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=14,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=14,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc)
```
